---
title: "Partial peptides"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='images/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

## Load the translated peptides

- Translate cDNA seuence - GCAT or Maker with ORFfinder
- Minimum ORF must be 30aa
- Keep only the complete sequences, avoid partial even if those are longer
- Keep all the peptides within a range og 10aa from the longer. Multiple isoforms possible for the same target?

```{r load_data}
library( dplyr )
library( ggplot2 )
library( tidyr )
library( data.table )
library(plyr)

maker <- read.delim("/projects/btl_scratch/kgagalova/TargetSetKollector/cdhit-4/Peptides/PeptidesMaker/LenPeptides.txt", header=FALSE)
gcat <- read.delim("/projects/btl_scratch/kgagalova/TargetSetKollector/cdhit-4/Peptides/PeptidesGCAT/LenPeptides.txt", header=FALSE)

maker$type = as.factor(rep("maker",nrow(maker)))
gcat$type = as.factor(rep("gcat",nrow(gcat)))

peptides = rbind(maker,gcat)
colnames(peptides)[c(1,2)] = c("len","pept_nam")

#get multeplicity per peptide
peptides$target = sapply(strsplit(as.character(peptides$pept_nam), "_product_"), "[[", 2)

freq_makerTargets = cbind(unname(table(subset(peptides,peptides$type=="maker")$target)), rep("maker",nrow(table(subset(peptides,peptides$type=="maker")$target))))
freq_gcatTargets = cbind(unname(table(subset(peptides,peptides$type=="gcat")$target)), rep("gcat",nrow(table(subset(peptides,peptides$type=="gcat")$target))))

freqTargets = as.data.frame(rbind(freq_gcatTargets, freq_makerTargets))
colnames(freqTargets) = c("counts","type")
freqTargets$counts = as.numeric(as.character(freqTargets$counts))
```

## Plots
Plot the lengts per group of peptides, GCAT vs Maker

```{r peptides_len}
cdat <- ddply(peptides, "type", summarise, rating.med=median(len))
cdat

ggplot(peptides, aes(x=len, fill=type)) + geom_density(alpha=.3) +
    geom_vline(data=cdat, aes(xintercept=rating.med,  colour=type),
               linetype="dashed", size=1)

ggplot(peptides, aes(x=len, fill=type)) + geom_histogram(alpha=.5) +
    geom_vline(data=cdat, aes(xintercept=rating.med,  colour=type),
               linetype="dashed", size=1)

#plot multeplicity within the type of targets
ggplot(freqTargets, aes(x=counts, fill=type)) +
    geom_histogram(position="dodge",stat="count")
```

## Some examples

- GCAT clear threshold
```
#413     lcl|ORF1_1:195:1436_unnamed_protein_product
#138     lcl|ORF36_1:1211:795_unnamed_protein_product
#132     lcl|ORF17_1:1145:1543_unnamed_protein_product
#106     lcl|ORF15_1:569:889_unnamed_protein_product
#87    lcl|ORF29_1:1527:1264_unnamed_protein_product
#79    lcl|ORF38_1:629:390_unnamed_protein_product
#71    lcl|ORF5_1:421:636_unnamed_protein_product
#62    lcl|ORF33_1:318:130_unnamed_protein_product
#60    lcl|ORF12_1:140:322_unnamed_protein_product
#58    lcl|ORF16_1:968:1144_unnamed_protein_product
```

- Maker unclear pattern, non complete peptide, likely truncated peptide at the top?

```
#1074
lcl|ORF1_augustus_masked-160355095-processed-gene-0.0-mRNA-1:0:3224_unnamed_protein_product,_partial
#106
lcl|ORF73_augustus_masked-160355095-processed-gene-0.0-mRNA-1:1876:1556_unnamed_protein_product
#85
lcl|ORF68_augustus_masked-160355095-processed-gene-0.0-mRNA-1:3157:2900_unnamed_protein_product
#82
lcl|ORF46_augustus_masked-160355095-processed-gene-0.0-mRNA-1:3185:2937_unnamed_protein_product
#80
lcl|ORF55_augustus_masked-160355095-processed-gene-0.0-mRNA-1:1568:1326_unnamed_protein_product
#78
lcl|ORF85_augustus_masked-160355095-processed-gene-0.0-mRNA-1:2820:2584_unnamed_protein_product
#71
lcl|ORF3_augustus_masked-160355095-processed-gene-0.0-mRNA-1:301:516_unnamed_protein_product
```

## From Austin
- It is important to have a high quality set of proteins
- Check the longerst partial ones and see if I can take them back by aligning to proteins and see if their 5 prime is there
- Exclude the ones with multiple complete and shorter ORFs.