---
title: "BUSCO multiplicity analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='images/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

## PG29

Analysis is performed on PG29 reconstrucetd genes. Note that some iterations are still missing for bin 8.
Extract only the targets that are highlighted by BUSCO.


```{r load_PG29_data}
library( dplyr )
library( ggplot2 )
library( tidyr )
library( data.table )

dataPath="/projects/btl/kgagalova/PHD_projects/SpruceUp/KollectorGeneReconstruction3species/RunKollector/data/CoverageKollectorPG29"
allFiles <- list.files( path = dataPath, pattern = ".out", full.names = TRUE )

l <- lapply( allFiles, function( fn ){
  d <- read.table( fn, header = F );
  d$fileName <- fn;
  d
  } );

dPG29 <- bind_rows( l );
dim(dPG29)
dPG29$bin = sapply(strsplit(sapply(strsplit(dPG29$fileName,"/"),"[[",11),"\\="),"[[",1)
dPG29$iteration = gsub("iteration.", "", gsub(".out","",sapply(strsplit(sapply(strsplit(dPG29$fileName,"/"),"[[",11),"\\="),"[[",2)))
colnames(dPG29)[c(1:3)] = c("cov","trans","contig")
dPG29 <- dPG29 %>% filter(cov != 0)
dPG29$sr <- ifelse(dPG29$cov >= .90, "Succeeded","Failed" )

#calculate the number of contigs per target
d1PG29 = dPG29 %>% group_by( trans,iteration ) %>% summarize( freq = n(),cov_mean = mean(cov), cov_std = sd(cov) )
d1PG29$freq = as.factor(d1PG29$freq)
#replace NA in sd
d1PG29$cov_std[which(is.na(d1PG29$cov_std))] <- 0
head(d1PG29)
```

## WS77111

```{r load_WS_data}
dataPath="/projects/btl/kgagalova/PHD_projects/SpruceUp/KollectorGeneReconstruction3species/RunKollector/data/CoverageKollectorWS"
allFiles <- list.files( path = dataPath, pattern = ".out", full.names = TRUE )

l <- lapply( allFiles, function( fn ){
  d <- read.table( fn, header = F );
  d$fileName <- fn;
  d
  } );

dWS <- bind_rows( l );
dim(dWS)
dWS$bin = sapply(strsplit(sapply(strsplit(dWS$fileName,"/"),"[[",11),"\\="),"[[",1)
dWS$iteration = gsub("iteration.", "", gsub(".out","",sapply(strsplit(sapply(strsplit(dWS$fileName,"/"),"[[",11),"\\="),"[[",2)))
colnames(dWS)[c(1:3)] = c("cov","trans","contig")
dWS <- dWS %>% filter(cov != 0)
dWS$sr <- ifelse(dWS$cov >= .90, "Succeeded","Failed" )

#calculate the number of contigs per target
d1WS = dWS %>% group_by( trans,iteration ) %>% summarize( freq = n(),cov_mean = mean(cov), cov_std = sd(cov) )
d1WS$freq = as.factor(d1WS$freq)
#replace NA in sd
d1WS$cov_std[which(is.na(d1WS$cov_std))] <- 0
head(d1WS)
```


Load the list of targets by BUSCO.

```{r load_busco}
busco = read.table("/projects/spruceup/pglauca/WS77111/analyses/comparative-genomics/kollector/experiment/single-copy/targets-single-copy-busco-in-pg29v4.txt",header=F)
#intersect with contigs list
busco$V1 = as.character(busco$V1)
#####################PG29
d1PG29_busco = d1PG29[which(d1PG29$trans%in% busco$V1),]
#how many of the busco transcripts are found in the target set
length(unique(d1PG29_busco$trans)) #out of 317
#which one is not present here
busco$V1[!(busco$V1 %in% unique(unique(d1PG29_busco$trans)))]
#success rate overall
dPG29_busco = dPG29[which(dPG29$trans%in% busco$V1),]
buscoPG29_sr = subset(dPG29_busco,dPG29_busco$cov >= 0.90)
#distribution per iteration
table(buscoPG29_sr$iteration)
#total success rate
sum(table(buscoPG29_sr$iteration))
d2PG29 = merge(dPG29_busco[,c("trans","cov","iteration")],d1PG29[which(d1PG29$trans %in% as.character(busco$V1)),],by=c("trans","iteration"))



#####################WS77111
d1WS_busco = d1WS[which(d1WS$trans%in% busco$V1),]
#how many of the busco transcripts are found in the target set
length(unique(d1WS_busco$trans)) #out of 317
#which one is not present here
busco$V1[!(busco$V1 %in% unique(unique(d1WS_busco$trans)))]
#success rate overall
dWS_busco = dWS[which(dWS$trans%in% busco$V1),]
buscoWS_sr = subset(dWS_busco,dWS_busco$cov >= 0.90)
#distribution per iteration
table(buscoWS_sr$iteration)
#total success rate
sum(table(buscoWS_sr$iteration))
d2WS = merge(dWS_busco[,c("trans","cov","iteration")],d1WS[which(d1WS$trans %in% as.character(busco$V1)),],by=c("trans","iteration"))
```

Plot the number of contigs per target - single dot, single coverage value

```{r busco_boxplot}
d2PG29$freq = as.factor(d2PG29$freq)
ggplot(d2PG29, aes(freq,cov)) +
    geom_boxplot(outlier.size=NA) +
    geom_jitter(aes(freq,cov),
               position=position_jitter(width=0.1,height=0),
               alpha=0.6,
               size=3,
               colour="darkblue") +
    xlab("Number of reconstruceted genes per target") +
    ylab("Coverage - BUSCO PG29") +
    theme(axis.title.x = element_text(face='bold',size=16,hjust=0.5),
          axis.title.y = element_text(face='bold',size=16,vjust=1),
          axis.text.x = element_text(face='bold',size=14,color='black'),
          axis.text.y = element_text(face='bold',size=14,color='black')) + 
    facet_wrap( ~ iteration ) + 
    geom_hline(yintercept = 0.9,colour="red",linetype="dashed")

d2WS$freq = as.factor(d2WS$freq)
ggplot(d2WS, aes(freq,cov)) +
    geom_boxplot(outlier.size=NA) +
    geom_jitter(aes(freq,cov),
               position=position_jitter(width=0.1,height=0),
               alpha=0.6,
               size=3,
               colour="red") +
    xlab("Number of reconstruceted genes per target") +
    ylab("Coverage - BUSCO WS") +
    theme(axis.title.x = element_text(face='bold',size=16,hjust=0.5),
          axis.title.y = element_text(face='bold',size=16,vjust=1),
          axis.text.x = element_text(face='bold',size=14,color='black'),
          axis.text.y = element_text(face='bold',size=14,color='black')) + 
    facet_wrap( ~ iteration ) + 
    geom_hline(yintercept = 0.9,colour="red",linetype="dashed")

```

Plot the number of contigs per target - mean value for coverage

```{r mean_coverage_busco}
ggplot(d1WS_busco, aes(freq,cov_mean,colour=cov_std)) +
    geom_boxplot(outlier.size=NA) +
    geom_jitter(aes(freq,cov_mean),
               position=position_jitter(width=0.1,height=0),
               alpha=0.6,
               size=3) +
    xlab("Number of reconstruceted genes per target") +
    ylab("Mean coverage - BUSCO WS") +
    theme(axis.title.x = element_text(face='bold',size=16,hjust=0.5),
          axis.title.y = element_text(face='bold',size=16,vjust=1),
          axis.text.x = element_text(face='bold',size=14,color='black'),
          axis.text.y = element_text(face='bold',size=14,color='black')) + 
    facet_wrap( ~ iteration ) + 
    geom_hline(yintercept = 0.9,colour="red",linetype="dashed") + 
    scale_colour_gradientn(colours = terrain.colors(10))

ggplot(d1PG29_busco, aes(freq,cov_mean,colour=cov_std)) +
    geom_boxplot(outlier.size=NA) +
    geom_jitter(aes(freq,cov_mean),
               position=position_jitter(width=0.1,height=0),
               alpha=0.6,
               size=3) +
    xlab("Number of reconstruceted genes per target") +
    ylab("Mean coverage - BUSCO PG29") +
    theme(axis.title.x = element_text(face='bold',size=16,hjust=0.5),
          axis.title.y = element_text(face='bold',size=16,vjust=1),
          axis.text.x = element_text(face='bold',size=14,color='black'),
          axis.text.y = element_text(face='bold',size=14,color='black')) + 
    facet_wrap( ~ iteration ) + 
    geom_hline(yintercept = 0.9,colour="red",linetype="dashed") + 
    scale_colour_gradientn(colours = terrain.colors(10))
```


## Summary

- The contigs in PG29 with some coverage detected cover 316 of the 317 BUSCO transcripts. In WS 315.
- The overall success rate for PG29 is 195 (coverage > 0.9): iteration 1 - 163, iteration 2 - 12, iteration 3 - 9, iteration 4 - 6, iteration 5 - 5. For WS is respectively 167, 27, 6, 15 and 9
- There are few genes that are successful and have partial reconstruction with another target.
- Note that whenever the reconstruction is successful for multiple contigs, there is large difference between the coverage of the different contigs. 